Tennis doubles and ghosts

### 2025-12-03 inst/tennis.Rmd
soft link for hyper2.bib
consistentification: use specificp.gt.test() if possible

---
title: "Tennis doubles and ghosts"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

```{r specificptesthere,cache=TRUE}
specificp.test(tennis_ghost,"G",0.0001)  # nonzero value needed to avoid triggering known R bug
```

>>>>

---
title: "Tennis doubles and ghosts"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

```{r specificptesthere,cache=TRUE}
specificp.gt.test(tennis_ghost,"G",0)  
```
